---
title: "homework-03"
author: "Chun Pong Brian Chan"
date: "10/04/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nycflights13)
library(dplyr)
library(ggplot2)
```

## 1

```{r}
flights2 <- flights %>%
  group_by(dep_time) %>%
  summarise(dep_delay = sum(dep_delay, na.rm = TRUE), arr_delay = sum(arr_delay, na.rm = TRUE)) %>%
  arrange(dep_delay, arr_delay)
head(flights2)
```
With this result, I believe the best time to avoid delay is around 6am in the morning since it takes less time the the schedule time to arrive, that is why it has a negative value for both depature and arrival delay.


## 2a
```{r}
flights2 <- flights %>%
  group_by(carrier) %>%
  summarise(dep_delay = sum(dep_delay, na.rm = TRUE), arr_delay = sum(arr_delay, na.rm = TRUE))

ggplot(flights2, aes(carrier, dep_delay)) +
  labs(title = "Total Departure Delay Time on Each Carrier", 
       y = "Total Departure Delay Time", 
       x = "Carrier") + 
  geom_point() 

```
There are certain carrier has way higher total departure delay time, which are EV, B6, and UA, customers that use these three airlines are more likely to experience departure delay than those that using other airlines.

## 2b
```{r}
flights2 <- flights %>%
  group_by(origin) %>%
  summarise(dep_delay = sum(dep_delay, na.rm = TRUE), arr_delay = sum(arr_delay, na.rm = TRUE))

ggplot(flights2, aes(origin, dep_delay)) +
  labs(title = "Total Departure Delay Time for Each Original Airport", 
       y = "Total Departure Delay Time", 
       x = "Airport") + 
  geom_point()
```
The most likely EWR airport has the highest chance of delaying flights than other airports.



## 2c
```{r}
flights2 <- flights %>%
  group_by(dest) %>%
  summarise(dep_delay = sum(dep_delay, na.rm = TRUE), arr_delay = sum(arr_delay, na.rm = TRUE)) %>%
  arrange(dep_delay)

ggplot(flights2, aes(dest, dep_delay)) +
  labs(title = "Total Departure Delay Time on Each Destination", 
       y = "Total Departure Delay Time", 
       x = "Destination") + 
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  geom_point()
```
ORD, ATL, and SFO has the highest total departure delay time among all the airports in the states. I believe one of the reasons is that these three airports are the biggest airports in the states, which means that they need to handle a lot more flights than a lot of the other airports in comparison, which makes them have a higher chance of delaying their flights.
















